A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-30 paper.tex
minor changes

% TODO: see if anyone else used diffusion to couple neurons
 Following *** references are Collins and Richmond which you have and Yanagita T, Ichinomiya T, Oyama Y. Pair of excitable Fitzhugh-Nagumo elements: Synchronization, multistability, and chaos. Physical Review E. 2005 Nov 28;72(5):056218. , we now use 
generalized diffusion coupling between FHN neurons to model gap junctions and synapses. The effect of gap junctions and synapses upon the membrane potential is modeled by replacing the external current $I_\mathrm{ext}$ of the system, by a generalized diffusion term $D \max(Δv,0)$. A positive diffusion coefficient $D$ is used to simulate a gap junction, or an excitatory synapse and a negative coefficient to simulate an inhibitory synapse (\citet{collins1994}).

>>>>

% TODO: see if anyone else used diffusion to couple neurons
 Following *** references are Collins and Richmond which you have and Yanagita T, Ichinomiya T, Oyama Y. Pair of excitable Fitzhugh-Nagumo elements: Synchronization, multistability, and chaos. Physical Review E. 2005 Nov 28;72(5):056218. , we now use 
generalized diffusion coupling between FHN neurons to model gap junctions and synapses. The effect of gap junctions and synapses upon the membrane potential is modeled by replacing the external current $I_\mathrm{ext}$ of the system, by a generalized diffusion term, $D \max(Δv,0)$. A positive diffusion coefficient $D$ is used to simulate a gap junction, or an excitatory synapse and a negative coefficient to simulate an inhibitory synapse (\citet{collins1994}).
